\documentclass{article}
\begin{document}
{\Large \begin{center}\textbf{LEAP Math Placement Info}\end{center}}
\noindent{\large\textbf{Placement Codes}}
\begin{description}
\item[No placement] The student did not take the math placement test, and did not show any indication of having an interest in math.\\ \emph{Recommendation}: No math course Fall semester, possibly MAT 217 Applied Stats in Winter depending on major.
\item[MAT111] The student is ready to take MAT111 Calc with Review.\\ \emph{Recommendation}: Depending on major, MAT111 or delay AFR choice.
\item[MAT121] The student is ready to take MAT121 Calc I.\\ \emph{Recommendation}: Depending on major, MAT121 or delay AFR choice.
\item[MAT121+] The student scored particularly well in the placement test, and would qualify for starting beyond MAT121, with MAT122 or higher, should they choose to.\\ \emph{Recommendation}: Student encouraged to pursue math further. Discuss with math department member whether to start at MAT121 or MAT122.
\item[see dept] The student either indicated that they did not have pre-calc knowledge, or performed poorly on online placement test.\\ \emph{Recommendation}: If student is interested in taking Calculus, they should consult a math department member. Otherwise, delay AFR choice.
\end{description}
\vfill
{\large\textbf{Winter Course times}}
\begin{description}
\item[MAT112 Calc with Review (cont)] TR 8am-10am. Students who take MAT111 in the Fall should avoid Great Works at that time.
\item[MAT122 Calc II] MTWF 10am--11am. Students who might want to consider continuing with Calc II should avoid Great Works at that time.
\item[MAT221 Calc III] MTWR 1pm--2pm. Students starting at Calc II who intend to continue with Calc III should avoid Great Works at that time.
\end{description}
\vfill
\end{document}